LEGWORK: A python package for computing the evolution and detectability \\ of stellar-origin gravitational-wave sources with space-based detectors

### 2022-02-06 src/ms.tex
add orb subscripts

\begin{equation}{\lwFuncURL{strain}{amplitude_modulation}}
    A_{\rm{mod}}^{2}=\frac{1}{2} \left[\left(1+\cos ^{2} \iota\right)^{2}\left\langle F_{+}^{2}\right\rangle+4 \cos ^{2} \iota\left\langle F_{\times}^{2}\right\rangle\right],
\label{eq:amp_mod}
\end{equation}
where $\left\langle F_{+}^{2}\right\rangle$ and $\left\langle F_{\times}^{2}\right\rangle$, the orbit-averaged detector responses, are defined as
\begin{equation}{\lwFuncURL{utils}{F_plus_squared}}
    \begin{split}
        \avg{ F_{+}^{2}} = \frac{1}{4}\big(\cos ^{2} 2 \psi\left\langle D_{+}^{2}\right\rangle &-\sin 4 \psi\left\langle D_{+} D_{\times}\right\rangle\\
        &+\sin ^{2} 2 \psi\left\langle D_{\times}^{2}\right\rangle\big),
    \end{split}
\label{eq:response_fplus}
\end{equation}

\begin{equation}{\lwFuncURL{utils}{F_cross_squared}}
    \begin{split}
        \avg{ F_{\times}^{2}} = \frac{1}{4}\big(\cos^{2} 2 \psi \avg{ D_{\times}^{2}} &+\sin 4 \psi \avg{ D_{+} D_{\times}}\\
        &+\sin ^{2} 2 \psi \avg{ D_{+}^{2}} \big),
    \end{split}
\label{eq:response_fcross}
\end{equation}
and
\begin{equation}{\lwFuncURL{utils}{D_plus_D_cross}}
    \begin{split}
        \avg{ D_{+} D_{\times}} = \frac{243}{512} \cos \theta \sin 2 \phi &\left(2 \cos ^{2} \phi-1\right) \\ &\times \left(1+\cos ^{2} \theta\right),
    \end{split}
\label{eq:d_plus_cross}
\end{equation}
\begin{equation}{\lwFuncURL{utils}{D_cross_squared}}
    \begin{split}
        \avg{ D_{\times}^{2}} = \frac{3}{512}\big(120 \sin ^{2} \theta &+\cos ^{2} \theta \\
        &+162 \sin ^{2} 2 \phi \cos ^{2} \theta\big),
    \end{split}
\label{eq:d_cross}
\end{equation}
\begin{equation}{\lwFuncURL{utils}{D_plus_squared}}
    \begin{split}
        \avg{ D_{+}^{2} } =  \frac{3}{2048}\big[&487+158 \cos ^{2} \theta+7 \cos ^{4} \theta\\
        &-162 \sin ^{2} 2 \phi\left(1+\cos ^{2} \theta\right)^{2}\big].
    \end{split}
\label{eq:d_plus}
\end{equation}
The orbital motion of LISA smears the source frequency by roughly $10^{-4}\,\rm{mHz}$ due to the antenna pattern changing as the detector orbits, the Doppler shift from the motion, and the phase modulation from the $+$ and $\cross$ polarisations in the antenna pattern. Generally, the modulation reduces the strain amplitude because the smearing in frequency reduces the amount of signal build up at the true source frequency.

>>>>

\begin{equation}{\lwFuncURL{strain}{amplitude_modulation}}
    A_{\rm{mod}}^{2}=\frac{1}{2} \left[\left(1+\cos ^{2} \iota\right)^{2}\left\langle F_{+}^{2}\right\rangle_{\rm \referee{orb}}+4 \cos ^{2} \iota\left\langle F_{\times}^{2}\right\rangle_{\rm \referee{orb}}\right],
\label{eq:amp_mod}
\end{equation}
where $\left\langle F_{+}^{2}\right\rangle_{\rm \referee{orb}}$ and $\left\langle F_{\times}^{2}\right\rangle_{\rm \referee{orb}}$, the orbit-averaged detector responses, are defined as
\begin{equation}{\lwFuncURL{utils}{F_plus_squared}}
    \begin{split}
        \avg{ F_{+}^{2}}_{\rm \referee{orb}} = \frac{1}{4}\big(&\cos ^{2} 2 \psi\left\langle D_{+}^{2}\right\rangle_{\rm \referee{orb}} \\
        -&\sin 4 \psi\left\langle D_{+} D_{\times}\right\rangle_{\rm \referee{orb}}\\
        +&\sin ^{2} 2 \psi\left\langle D_{\times}^{2}\right\rangle_{\rm \referee{orb}}\big),
    \end{split}
\label{eq:response_fplus}
\end{equation}

\begin{equation}{\lwFuncURL{utils}{F_cross_squared}}
    \begin{split}
        \avg{ F_{\times}^{2}} = \frac{1}{4}\big(&\cos^{2} 2 \psi \avg{ D_{\times}^{2}}_{\rm \referee{orb}}\\
        +&\sin 4 \psi \avg{ D_{+} D_{\times}}_{\rm \referee{orb}}\\
        +&\sin ^{2} 2 \psi \avg{ D_{+}^{2}}_{\rm \referee{orb}} \big),
    \end{split}
\label{eq:response_fcross}
\end{equation}
and
\begin{equation}{\lwFuncURL{utils}{D_plus_D_cross}}
    \begin{split}
        \avg{ D_{+} D_{\times}}_{\rm \referee{orb}} = \frac{243}{512} \cos \theta \sin 2 \phi &\left(2 \cos ^{2} \phi-1\right) \\ &\times \left(1+\cos ^{2} \theta\right),
    \end{split}
\label{eq:d_plus_cross}
\end{equation}
\begin{equation}{\lwFuncURL{utils}{D_cross_squared}}
    \begin{split}
        \avg{ D_{\times}^{2}}_{\rm \referee{orb}} = \frac{3}{512}\big(120 \sin ^{2} \theta &+\cos ^{2} \theta \\
        &+162 \sin ^{2} 2 \phi \cos ^{2} \theta\big),
    \end{split}
\label{eq:d_cross}
\end{equation}
\begin{equation}{\lwFuncURL{utils}{D_plus_squared}}
    \begin{split}
        \avg{ D_{+}^{2} }_{\rm \referee{orb}} =  \frac{3}{2048}\big[&487+158 \cos ^{2} \theta+7 \cos ^{4} \theta\\
        &-162 \sin ^{2} 2 \phi\left(1+\cos ^{2} \theta\right)^{2}\big].
    \end{split}
\label{eq:d_plus}
\end{equation}
The orbital motion of LISA smears the source frequency by roughly $10^{-4}\,\rm{mHz}$ due to the antenna pattern changing as the detector orbits, the Doppler shift from the motion, and the phase modulation from the $+$ and $\cross$ polarisations in the antenna pattern. Generally, the modulation reduces the strain amplitude because the smearing in frequency reduces the amount of signal build up at the true source frequency.
